---
title: "CaravanHealth"
author: "Amy Jung"
date: '2022-04-26'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::knit_engines$set(problem_description = function(options) {
  code <- paste(options$code, collapse = "\n")
})
```


```{r load packages, message = FALSE}
library(data.table)

library(sandwich)
library(lmtest)

library(AER) 

library(ggplot2) 
library(patchwork)

library(stargazer)
library(cregg)
```

## Load Data

```{r pressure, echo=FALSE}
d = fread('~/CaravanHealth-HW/maternity_claims_2017.csv')
d
```

## Regression

### Model 1: only length_of_stay

The intuition is that length_of_stay would be the best indicator of total_claim_cost (more time at hospital = greater cost).

Null hypothesis: no correlation between length_of_stay and total_claim_cost. 

```{r model 1, echo=TRUE}
# model with only length_of_stay

mod_1 = lm(total_claim_cost ~ 
                 length_of_stay, data=d)

mod_1$cluster_se <- sqrt(diag(vcovCL(mod_1)))

stargazer(
  mod_1, 
  se = list(mod_1$cluster_se), 
  type = 'text'
)
```

Interpretation: The correlation between length_of_stay and total_claim_cost is a statistically significant. An increase in 1 day in the hospital leads to an increase in $4,228.16 in claim costs, according to model 1. 



### Model 2: length_of_stay + icd_10_diagnosis_code + zip_code + patient_age

The intuition is that icd_10_diagnosis_code, zip_code, and patient_age would also have an impact on total_claim_costs -- with ICD codes used for billing purposes, zip codes relating to SDH (social determinants of health), and patient age maybe correlating with more procedures needed for older mothers. 

```{r basic model, echo=TRUE}
# model with other variables 

mod_2 = lm(total_claim_cost ~ 
                 length_of_stay + 
                 icd_10_diagnosis_code + 
                 as.factor(zip_code) + 
                 patient_age, 
               data=d)

mod_2$cluster_se <- sqrt(diag(vcovCL(mod_2)))

stargazer(
  mod_2, 
  se = list(mod_2$cluster_se), 
  type = 'text'
)
```

Model 2 Constant is when: ICD code O03, length of stay 0, patient age 0, zip code 35896.

Interpretation: The correlation of length_of_stay, icd_10_diagnosis_code, patient_age to total_claim_cost is statistically significant. The correlation between zip_code and total_claim_cost is not significant. 

Interesting insights according to Model 2:
- with the other variables factored in (compared to Model 1), the coefficient for length_of_stay decreases by 60% (from 4,228.162 to 2,452.569), which indicates omitted variable bias in Model 1
- ICD code O80 has a negative significant coefficient (-9,072.846)
- an increase in patient age decreases total_claim_cost (-18.152)



